---
title: "Week 7"
author: "Miranda Gilbert"
date: "9/2/2019"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library(nycflights13)
library(babynames)
library(maps)
```

##13.2.1 Exercises

  1. I would want to combine flights and airports because flights has the origin and destination and airports has the longitude and latitude needed for mapping. 
  
  2. faa and origin connect between airports and flights, so the same connection can be made between faa and the origin in weathers. 
  
  3. If there were weather records for every airport then weather could also be connected to destination. 
  
  4. I would create a new table with month, day, and year of special holidays that people fly less during. My new table would connect to the month, day, and year in flights and weather. 
  
##13.3.1 Exercises
  
  1. 
  
```{r}
flights %>%
  mutate(index = row_number()) %>%
  select(index, everything())
```


  2a. playerID, yearID, and stint are all keys for the Lahman::batting data. playerID and yearID are not primary keys becuse a player can play on different teams in the same year. 
  
  
  2b. year, sex, and name are all keys for the babynames::babynames data set. Year and name are not promary keys because babues with the same name can be born in the same year.
  
##13.4.6 Exercises

  1.
  Spatial distribution of delays
```{r}
airports %>%
  semi_join(flights, c("faa" = "dest")) %>%
  ggplot(aes(lon, lat)) +
    borders("state") +
    geom_point() +
    coord_quickmap()
```

```{r}
flights %>% group_by(dest) %>%
  summarize(avg_arr_delay = mean(arr_delay, na.rm = TRUE)) %>%
  left_join(airports, by = c('dest' = 'faa')) %>%
  ggplot(aes(x = lon, y = lat, size = avg_arr_delay, color = avg_arr_delay)) +
  borders('state') +
  geom_point() +
  coord_quickmap()
```
Average delays per airport

  2. 
```{r}
flights %>% 
  left_join(airports, by = c('dest' = 'faa')) %>%
  left_join(airports, by = c('origin' = 'faa'), suffix = c('.dest', '.origin')) %>%
  select(dest, origin, contains('lat'), contains('lon'))
```
  
##13.5.1

  2. 
```{r}
 flights_100 <- flights %>%
  filter(!is.na(dep_delay)) %>%
  group_by(tailnum) %>%
  summarize(n = n()) %>%
  filter(n > 100)

flights %>%
  semi_join(flights_100, by = 'tailnum')
```

  4. 48 hours of worst delays cross referened with weather
```{r}
worst_hours <- flights %>%
   group_by(origin, year, month, day, hour) %>%
  summarise(dep_delay = mean(dep_delay, na.rm = TRUE)) %>%
  ungroup() %>%
  arrange(desc(dep_delay)) %>%
  slice(1:48)
weather_most_delayed <- semi_join(weather, worst_hours,
  by = c(
    "origin", "year",
    "month", "day", "hour"
  )
)
select(weather_most_delayed, temp, wind_speed, precip) %>%
  print(n = 48)

```

```{r}
ggplot(weather_most_delayed, aes(x = precip, y = wind_speed, color = temp)) +
  geom_point()
```

##28.2.1
  
  1. 
```{r}
 ggplot(mpg, aes(cyl, cty)) +     geom_point(aes(color = year))     +  geom_smooth(se=FALSE) + labs(title = "City miles decreasing as cylinder number increases",
    subtitle = "Year seemed to have to impact on city miles or cylinder number",
    caption = "Data from fueleconomy.gov",
    x = "Cylinder Number",
    y = " City Miles per Gallon"
  )
                                                  
```

##28.4.4

  1. It does not override the default scale because the colors in geom_hex() are set by the fill aesthetic, not the color aesthetic.
  
  4. 
```{r}
ggplot(diamonds, aes(carat, price)) +
  geom_point(aes(colour = cut), alpha = 1 / 20) +
  theme(legend.position = "bottom") +
  guides(colour = guide_legend(nrow = 1, override.aes = list(alpha = 1)))
```

