---
title: "Week 4"
author: "Miranda Gilbert"
date: "7/29/2019"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##7.3.4 Exercises
  1. 
``` 
ggplot(data = diamonds, mapping = aes(x = x)) + geom_histogram(binwidth = 30)
```

```
ggplot(data = diamonds, mapping = aes(x = y)) + geom_histogram(binwidth = 30)
```
```
ggplot(data = diamonds, mapping = aes(x = z)) + geom_histogram(binwidth = 30)
```
There are more small diamonds than large diamonds.Diamonds are usually wider than they are tall or deep, so I would suppose the larger numbers are width and the smaller are length and depth.

  2.
```{r}
ggplot(data = diamonds) +
  geom_histogram(mapping = aes(x = price), binwidth = 50)
```
There is nothing around the 1500 range which is surprising. 

  3. 
```{r}
diamonds %>% filter(between(carat, .96, 1.05)) %>%
  group_by(carat) %>% summarize(count = n())
```
There are 23 .99 carrat diamonds and 1558 1 carrat diamonds. I am guessing because it looks nicer to have a 1 carat than .99 carat in the report.

  4. 
```{r}
ggplot(data = diamonds) +
  geom_histogram(mapping = aes(x = price), binwidth = 50) +
  coord_cartesian(xlim = c(0,5000), ylim = c(0,1600))
```
```{r}
ggplot(data = diamonds) +
  geom_histogram(mapping = aes(x = price)) +
  coord_cartesian(xlim = c(0,5000), ylim = c(0,1600))
```
```{r}
ggplot(data = diamonds) +
  geom_histogram(mapping = aes(x = price), binwidth = 50) +
  xlim(c(0,5000))
```

##7.4.1
  1. Histograms remove missing values as seen in an above chart. Bar graphs create a caegory for missing numbers. I am guessing because missing numbers cannot be numerically shown on a hustogram but can be grouped in a bar graph. 
  2. ne.ram determines if NA values are taken out before computing sum or mean by making ne.ram true or false. 
  
##7.5.1.1
  1. *describe this plz)*
```{r}
 nycflights13::flights %>% 
  mutate(
    cancelled = is.na(dep_time),
    sched_hour = sched_dep_time %/% 100,
    sched_min = sched_dep_time %% 100,
    sched_dep_time = sched_hour + sched_min / 60
  ) %>% 
  ggplot() +
  geom_boxplot(mapping = aes(x = cancelled, y = sched_dep_time))
```
  
  2.
```{r}
  diamonds %>%
  mutate(cut = as.numeric(cut),
         color = as.numeric(color),
         clarity = as.numeric(clarity)) %>%
  select(price, everything()) %>%
  cor()
```
Running a correlation matirx, carat is most correlated with price and therefore the most important determinant. There is a negative correlation with cut.

  3. 
```{r}
  nycflights13::flights %>% 
  mutate(
    cancelled = is.na(dep_time),
    sched_hour = sched_dep_time %/% 100,
    sched_min = sched_dep_time %% 100,
    sched_dep_time = sched_hour + sched_min / 60
  ) %>% 
  ggplot() +
  geom_boxploth(mapping = aes(y = cancelled, x = sched_dep_time))
```
x and y had to be flipped to show the plot correctly. 

  5. 
  Violin plot is a compact way to show continuous data by combining a density graph and a box plot.
  Histogram also shows a continuous variable, but the variables have to fit into bins.
  
##7.5.2
  One example of a categorical covatiation plot would be plotting the car types and the kind of drive they have and visualizing wiht geom_count()
  
##7.5.3
  I could probably use my sunflowers time versus growth as two continuous variables and I would visualize with the box plot.

  